\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{amsmath, amssymb}
\usepackage{hyperref}

\setlist[enumerate]{itemsep=0.8em, topsep=0.8em}
\setlist[itemize]{itemsep=0.3em, topsep=0.3em}

\begin{document}

\begin{center}
  {\Large \textbf{Database Systems}}\\[0.25em]
  {\large \textbf{SQL and Relational Model Quiz}}\\[0.5em]
\end{center}

\noindent\textbf{Instructions:}
\begin{itemize}
  \item Answer all questions.
  \item For Questions 1--5, choose the best option.
  \item For Questions 6--8, mark True or False.
  \item For Questions 9--10, write detailed answers with SQL examples where appropriate.
\end{itemize}

\vspace{0.5em}

\begin{enumerate}[label=\textbf{\arabic*.}]
  \item Which normal form eliminates transitive dependencies?
  \begin{enumerate}[label=(\Alph*)]
    \item First Normal Form (1NF)
    \item Second Normal Form (2NF)
    \item Third Normal Form (3NF)
    \item Boyce-Codd Normal Form (BCNF)
  \end{enumerate}

  \item Which SQL clause is used to filter groups created by GROUP BY?
  \begin{enumerate}[label=(\Alph*)]
    \item WHERE
    \item HAVING
    \item ORDER BY
    \item FILTER
  \end{enumerate}

  \item A foreign key constraint ensures:
  \begin{enumerate}[label=(\Alph*)]
    \item All values in a column are unique
    \item Values reference existing values in another table
    \item No NULL values exist in the column
    \item The column is indexed automatically
  \end{enumerate}

  \item Which type of JOIN returns all rows from both tables, matching where possible?
  \begin{enumerate}[label=(\Alph*)]
    \item INNER JOIN
    \item LEFT JOIN
    \item RIGHT JOIN
    \item FULL OUTER JOIN
  \end{enumerate}

  \item The ACID property ``Isolation'' ensures:
  \begin{enumerate}[label=(\Alph*)]
    \item Transactions are permanent once committed
    \item Database remains consistent after transactions
    \item Concurrent transactions don't interfere with each other
    \item Transactions complete entirely or not at all
  \end{enumerate}

  \item A primary key can contain NULL values. (True/False)

  \item The DELETE statement can be rolled back if within a transaction. (True/False)

  \item An index always improves query performance. (True/False)

  \item Explain database normalization and its purpose. Describe First, Second, and Third Normal Forms with examples of tables that violate each form and how to correct them.
  \vspace{8em}

  \item Discuss the ACID properties of database transactions. Explain each property and describe mechanisms databases use to ensure these properties are maintained.
  \vspace{8em}

\end{enumerate}

\end{document}