\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{amsmath, amssymb}
\usepackage{hyperref}

\setlist[enumerate]{itemsep=0.8em, topsep=0.8em}
\setlist[itemize]{itemsep=0.3em, topsep=0.3em}

\begin{document}

\begin{center}
  {\Large \textbf{Environmental Science}}\\[0.25em]
  {\large \textbf{Climate Change and Ecosystems Quiz}}\\[0.5em]
\end{center}

\noindent\textbf{Instructions:}
\begin{itemize}
  \item Answer all questions.
  \item For Questions 1--5, choose the best option.
  \item For Questions 6--8, mark True or False.
  \item For Questions 9--10, write detailed answers with scientific reasoning.
\end{itemize}

\vspace{0.5em}

\begin{enumerate}[label=\textbf{\arabic*.}]
  \item Which gas is the most significant contributor to the anthropogenic greenhouse effect?
  \begin{enumerate}[label=(\Alph*)]
    \item Methane (CH$_4$)
    \item Nitrous oxide (N$_2$O)
    \item Carbon dioxide (CO$_2$)
    \item Chlorofluorocarbons (CFCs)
  \end{enumerate}

  \item The term ``carbon sink'' refers to:
  \begin{enumerate}[label=(\Alph*)]
    \item A source of carbon emissions
    \item A reservoir that absorbs more carbon than it releases
    \item A method of carbon taxation
    \item Industrial carbon capture facilities only
  \end{enumerate}

  \item Ocean acidification is primarily caused by:
  \begin{enumerate}[label=(\Alph*)]
    \item Increased water temperature
    \item Absorption of atmospheric CO$_2$
    \item Agricultural runoff
    \item Oil spills
  \end{enumerate}

  \item Which of the following is a positive feedback loop in climate change?
  \begin{enumerate}[label=(\Alph*)]
    \item Increased cloud cover reflecting sunlight
    \item Melting ice reducing Earth's albedo
    \item Plants absorbing more CO$_2$ as levels rise
    \item Ocean absorption of heat
  \end{enumerate}

  \item The Paris Agreement aims to limit global temperature increase to:
  \begin{enumerate}[label=(\Alph*)]
    \item 1.0째C above pre-industrial levels
    \item 1.5째C to well below 2째C above pre-industrial levels
    \item 3째C above pre-industrial levels
    \item Pre-industrial levels exactly
  \end{enumerate}

  \item The greenhouse effect is entirely harmful and did not exist before human industrialization. (True/False)

  \item Coral bleaching events are primarily caused by elevated ocean temperatures. (True/False)

  \item Deforestation contributes to climate change by reducing carbon sequestration capacity. (True/False)

  \item Explain the carbon cycle and how human activities have disrupted this natural process. Discuss at least three major anthropogenic sources of carbon emissions.
  \vspace{8em}

  \item Analyze the impacts of climate change on biodiversity. Discuss specific examples of affected ecosystems and species, and evaluate potential conservation strategies.
  \vspace{8em}

\end{enumerate}

\end{document}