\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{amsmath, amssymb}
\usepackage{hyperref}

\setlist[enumerate]{itemsep=0.8em, topsep=0.8em}
\setlist[itemize]{itemsep=0.3em, topsep=0.3em}

\begin{document}

\begin{center}
  {\Large \textbf{Electrical Circuits}}\\[0.25em]
  {\large \textbf{DC Circuit Analysis Quiz}}\\[0.5em]
\end{center}

\noindent\textbf{Instructions:}
\begin{itemize}
  \item Answer all questions.
  \item For Questions 1--5, choose the best option.
  \item For Questions 6--8, mark True or False.
  \item For Questions 9--10, write detailed answers with circuit analysis.
\end{itemize}

\vspace{0.5em}

\begin{enumerate}[label=\textbf{\arabic*.}]
  \item Three resistors of 6$\Omega$ each are connected in parallel. What is the equivalent resistance?
  \begin{enumerate}[label=(\Alph*)]
    \item 18$\Omega$
    \item 6$\Omega$
    \item 2$\Omega$
    \item 0.5$\Omega$
  \end{enumerate}

  \item Kirchhoff's Current Law (KCL) states that:
  \begin{enumerate}[label=(\Alph*)]
    \item The sum of voltage drops around a closed loop is zero
    \item The sum of currents entering a node equals the sum leaving
    \item Power dissipated equals $I^2R$
    \item Voltage is proportional to current
  \end{enumerate}

  \item A 12V battery is connected to a 4$\Omega$ resistor. What power is dissipated?
  \begin{enumerate}[label=(\Alph*)]
    \item 3W
    \item 36W
    \item 48W
    \item 144W
  \end{enumerate}

  \item In a series circuit, which quantity remains the same through all components?
  \begin{enumerate}[label=(\Alph*)]
    \item Voltage
    \item Current
    \item Resistance
    \item Power
  \end{enumerate}

  \item The time constant of an RC circuit is:
  \begin{enumerate}[label=(\Alph*)]
    \item $R/C$
    \item $R \times C$
    \item $1/(R \times C)$
    \item $\sqrt{R \times C}$
  \end{enumerate}

  \item An ideal voltage source maintains constant voltage regardless of the current drawn. (True/False)

  \item Thevenin's theorem states any linear circuit can be replaced by a voltage source in parallel with a resistor. (True/False)

  \item The maximum power transfer occurs when load resistance equals source resistance. (True/False)

  \item Explain Kirchhoff's Voltage Law (KVL) and Kirchhoff's Current Law (KCL). Demonstrate how to apply both laws to analyze a circuit with multiple loops and nodes.
  \vspace{8em}

  \item Describe Thevenin's theorem and Norton's theorem. Explain the process to find Thevenin equivalent circuit and demonstrate the relationship between Thevenin and Norton equivalents.
  \vspace{8em}

\end{enumerate}

\end{document}