\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{amsmath, amssymb}
\usepackage{hyperref}

\setlist[enumerate]{itemsep=0.8em, topsep=0.8em}
\setlist[itemize]{itemsep=0.3em, topsep=0.3em}

\begin{document}

\begin{center}
  {\Large \textbf{Introduction to Statistics}}\\[0.25em]
  {\large \textbf{Probability and Inference Quiz}}\\[0.5em]
\end{center}

\noindent\textbf{Instructions:}
\begin{itemize}
  \item Answer all questions.
  \item For Questions 1--5, choose the best option.
  \item For Questions 6--8, mark True or False.
  \item For Questions 9--10, write detailed answers with calculations where appropriate.
\end{itemize}

\vspace{0.5em}

\begin{enumerate}[label=\textbf{\arabic*.}]
  \item If P(A) = 0.3 and P(B) = 0.4, and A and B are independent events, what is P(A $\cap$ B)?
  \begin{enumerate}[label=(\Alph*)]
    \item 0.70
    \item 0.12
    \item 0.10
    \item 0.58
  \end{enumerate}

  \item The Central Limit Theorem states that:
  \begin{enumerate}[label=(\Alph*)]
    \item All populations are normally distributed
    \item Sample means approach a normal distribution as sample size increases
    \item Larger samples always have smaller means
    \item The median equals the mean in all distributions
  \end{enumerate}

  \item A Type I error occurs when:
  \begin{enumerate}[label=(\Alph*)]
    \item Failing to reject a false null hypothesis
    \item Rejecting a true null hypothesis
    \item The sample size is too small
    \item The p-value is greater than alpha
  \end{enumerate}

  \item Which measure of central tendency is most resistant to outliers?
  \begin{enumerate}[label=(\Alph*)]
    \item Mean
    \item Median
    \item Mode
    \item Range
  \end{enumerate}

  \item A 95\% confidence interval means:
  \begin{enumerate}[label=(\Alph*)]
    \item 95\% of the data falls within the interval
    \item There is a 95\% probability the true parameter is in this specific interval
    \item 95\% of similarly constructed intervals would contain the true parameter
    \item The sample mean is 95\% accurate
  \end{enumerate}

  \item The standard deviation of a sampling distribution is called the standard error. (True/False)

  \item A p-value of 0.03 means there is a 3\% chance the null hypothesis is true. (True/False)

  \item Correlation implies causation between two variables. (True/False)

  \item Explain the difference between descriptive and inferential statistics. Provide examples of when each would be appropriate and discuss the role of sampling in making inferences about populations.
  \vspace{8em}

  \item Describe the process of hypothesis testing, including the null and alternative hypotheses, significance level, p-value, and decision rules. Use an example to illustrate each step.
  \vspace{8em}

\end{enumerate}

\end{document}