\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{amsmath, amssymb}
\usepackage{hyperref}

\setlist[enumerate]{itemsep=0.8em, topsep=0.8em}
\setlist[itemize]{itemsep=0.3em, topsep=0.3em}

\begin{document}

\begin{center}
  {\Large \textbf{Principles of Microeconomics}}\\[0.25em]
  {\large \textbf{Supply, Demand, and Market Equilibrium Quiz}}\\[0.5em]
\end{center}

\noindent\textbf{Instructions:}
\begin{itemize}
  \item Answer all questions.
  \item For Questions 1--5, choose the best option.
  \item For Questions 6--8, mark True or False.
  \item For Questions 9--10, write detailed answers with graphs where appropriate.
\end{itemize}

\vspace{0.5em}

\begin{enumerate}[label=\textbf{\arabic*.}]
  \item If the price of a good increases and quantity demanded decreases, this illustrates:
  \begin{enumerate}[label=(\Alph*)]
    \item A shift in the demand curve
    \item A movement along the demand curve
    \item A shift in the supply curve
    \item Market disequilibrium
  \end{enumerate}

  \item When two goods are substitutes, an increase in the price of one good will:
  \begin{enumerate}[label=(\Alph*)]
    \item Decrease demand for the other good
    \item Increase demand for the other good
    \item Have no effect on the other good
    \item Decrease supply of the other good
  \end{enumerate}

  \item A price ceiling set below the equilibrium price will result in:
  \begin{enumerate}[label=(\Alph*)]
    \item A surplus
    \item A shortage
    \item No change in quantity
    \item Increased producer surplus
  \end{enumerate}

  \item The price elasticity of demand measures:
  \begin{enumerate}[label=(\Alph*)]
    \item How much supply changes when price changes
    \item The responsiveness of quantity demanded to price changes
    \item The slope of the demand curve
    \item Consumer income levels
  \end{enumerate}

  \item If demand is inelastic, a price increase will:
  \begin{enumerate}[label=(\Alph*)]
    \item Decrease total revenue
    \item Increase total revenue
    \item Leave total revenue unchanged
    \item Cause quantity demanded to fall to zero
  \end{enumerate}

  \item An increase in consumer income will always shift the demand curve to the right. (True/False)

  \item At the equilibrium price, the quantity supplied equals the quantity demanded. (True/False)

  \item A technological improvement in production will shift the supply curve to the left. (True/False)

  \item Explain the difference between a change in demand and a change in quantity demanded. Discuss at least three factors that cause the demand curve to shift, with real-world examples.
  \vspace{8em}

  \item Using supply and demand analysis, explain the effects of a government-imposed minimum wage above the equilibrium wage. Discuss the potential benefits and drawbacks of this policy.
  \vspace{8em}

\end{enumerate}

\end{document}