\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{amsmath, amssymb}
\usepackage{hyperref}

\setlist[enumerate]{itemsep=0.8em, topsep=0.8em}
\setlist[itemize]{itemsep=0.3em, topsep=0.3em}

\begin{document}

\begin{center}
  {\Large \textbf{Introduction to Psychology}}\\[0.25em]
  {\large \textbf{Learning and Memory Quiz}}\\[0.5em]
\end{center}

\noindent\textbf{Instructions:}
\begin{itemize}
  \item Answer all questions.
  \item For Questions 1--5, choose the best option.
  \item For Questions 6--8, mark True or False.
  \item For Questions 9--10, write detailed answers with examples.
\end{itemize}

\vspace{0.5em}

\begin{enumerate}[label=\textbf{\arabic*.}]
  \item In Pavlov's classical conditioning experiments, the bell before conditioning was a:
  \begin{enumerate}[label=(\Alph*)]
    \item Conditioned stimulus
    \item Unconditioned stimulus
    \item Neutral stimulus
    \item Conditioned response
  \end{enumerate}

  \item Which type of reinforcement schedule produces the highest, most consistent rate of response?
  \begin{enumerate}[label=(\Alph*)]
    \item Fixed ratio
    \item Variable ratio
    \item Fixed interval
    \item Variable interval
  \end{enumerate}

  \item The ``serial position effect'' refers to the tendency to remember:
  \begin{enumerate}[label=(\Alph*)]
    \item Items at the beginning and end of a list better than middle items
    \item Emotional events more vividly
    \item Information learned in a specific location
    \item Names better than faces
  \end{enumerate}

  \item Which memory system has a capacity of approximately 7 $\pm$ 2 items?
  \begin{enumerate}[label=(\Alph*)]
    \item Sensory memory
    \item Short-term memory
    \item Long-term memory
    \item Procedural memory
  \end{enumerate}

  \item Retrograde amnesia involves:
  \begin{enumerate}[label=(\Alph*)]
    \item Inability to form new memories
    \item Loss of memories formed before the trauma
    \item Forgetting how to perform learned skills
    \item False memory formation
  \end{enumerate}

  \item Punishment and negative reinforcement refer to the same concept in operant conditioning. (True/False)

  \item The hippocampus is primarily involved in the formation of new declarative memories. (True/False)

  \item Eyewitness testimony is generally considered highly reliable due to the accuracy of human memory. (True/False)

  \item Compare and contrast classical conditioning and operant conditioning. Include the key researchers, mechanisms, and real-world applications of each.
  \vspace{8em}

  \item Describe the multi-store model of memory (Atkinson-Shiffrin model). Discuss its strengths and at least two criticisms, referencing alternative models where appropriate.
  \vspace{8em}

\end{enumerate}

\end{document}