\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{amsmath, amssymb}
\usepackage{hyperref}

\setlist[enumerate]{itemsep=0.8em, topsep=0.8em}
\setlist[itemize]{itemsep=0.3em, topsep=0.3em}

\begin{document}

\begin{center}
  {\Large \textbf{Financial Accounting}}\\[0.25em]
  {\large \textbf{Financial Statements and Analysis Quiz}}\\[0.5em]
\end{center}

\noindent\textbf{Instructions:}
\begin{itemize}
  \item Answer all questions.
  \item For Questions 1--5, choose the best option.
  \item For Questions 6--8, mark True or False.
  \item For Questions 9--10, write detailed answers with examples.
\end{itemize}

\vspace{0.5em}

\begin{enumerate}[label=\textbf{\arabic*.}]
  \item The accounting equation is expressed as:
  \begin{enumerate}[label=(\Alph*)]
    \item Assets = Liabilities - Equity
    \item Assets = Liabilities + Equity
    \item Assets + Liabilities = Equity
    \item Assets - Equity = Revenue
  \end{enumerate}

  \item Which financial statement reports a company's financial position at a specific point in time?
  \begin{enumerate}[label=(\Alph*)]
    \item Income Statement
    \item Balance Sheet
    \item Cash Flow Statement
    \item Statement of Retained Earnings
  \end{enumerate}

  \item Depreciation expense is recorded to:
  \begin{enumerate}[label=(\Alph*)]
    \item Increase cash reserves for asset replacement
    \item Allocate the cost of an asset over its useful life
    \item Reflect the current market value of an asset
    \item Reduce tax liability exclusively
  \end{enumerate}

  \item The current ratio measures:
  \begin{enumerate}[label=(\Alph*)]
    \item Profitability
    \item Liquidity
    \item Solvency
    \item Efficiency
  \end{enumerate}

  \item Under accrual accounting, revenue is recognized when:
  \begin{enumerate}[label=(\Alph*)]
    \item Cash is received
    \item An invoice is sent
    \item The earnings process is substantially complete and collection is reasonably assured
    \item The fiscal year ends
  \end{enumerate}

  \item An increase in accounts receivable represents a cash inflow on the cash flow statement. (True/False)

  \item LIFO inventory method results in lower net income during periods of rising prices compared to FIFO. (True/False)

  \item Goodwill is recorded when a company purchases another company for more than its net asset value. (True/False)

  \item Explain the differences between the three main financial statements: the income statement, balance sheet, and cash flow statement. How do they relate to each other?
  \vspace{8em}

  \item Describe the difference between cash basis and accrual basis accounting. Why do GAAP and IFRS require accrual accounting for most businesses? Provide examples illustrating the differences.
  \vspace{8em}

\end{enumerate}

\end{document}