\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{amsmath, amssymb}
\usepackage{hyperref}

\setlist[enumerate]{itemsep=0.8em, topsep=0.8em}
\setlist[itemize]{itemsep=0.3em, topsep=0.3em}

\begin{document}

\begin{center}
  {\Large \textbf{Nutrition Science}}\\[0.25em]
  {\large \textbf{Macronutrients and Metabolism Quiz}}\\[0.5em]
\end{center}

\noindent\textbf{Instructions:}
\begin{itemize}
  \item Answer all questions.
  \item For Questions 1--5, choose the best option.
  \item For Questions 6--8, mark True or False.
  \item For Questions 9--10, write detailed answers with scientific explanations.
\end{itemize}

\vspace{0.5em}

\begin{enumerate}[label=\textbf{\arabic*.}]
  \item Which macronutrient provides the most energy per gram?
  \begin{enumerate}[label=(\Alph*)]
    \item Carbohydrates (4 kcal/g)
    \item Proteins (4 kcal/g)
    \item Fats (9 kcal/g)
    \item Alcohol (7 kcal/g)
  \end{enumerate}

  \item The glycemic index measures:
  \begin{enumerate}[label=(\Alph*)]
    \item Total sugar content of a food
    \item How quickly a food raises blood glucose levels
    \item Fiber content relative to carbohydrates
    \item Insulin content of foods
  \end{enumerate}

  \item Essential amino acids are those that:
  \begin{enumerate}[label=(\Alph*)]
    \item Are needed in the largest quantities
    \item Cannot be synthesized by the body and must be obtained from diet
    \item Are found only in animal products
    \item Have the highest caloric value
  \end{enumerate}

  \item Which type of fatty acid is primarily associated with increased cardiovascular risk?
  \begin{enumerate}[label=(\Alph*)]
    \item Monounsaturated fatty acids
    \item Polyunsaturated fatty acids
    \item Trans fatty acids
    \item Omega-3 fatty acids
  \end{enumerate}

  \item The primary role of B vitamins in metabolism is as:
  \begin{enumerate}[label=(\Alph*)]
    \item Energy sources
    \item Structural components of cells
    \item Coenzymes in metabolic reactions
    \item Antioxidants
  \end{enumerate}

  \item Dietary fiber is completely digested and absorbed in the small intestine. (True/False)

  \item Complete proteins contain all essential amino acids in adequate amounts. (True/False)

  \item BMR (Basal Metabolic Rate) accounts for the majority of daily energy expenditure in sedentary individuals. (True/False)

  \item Explain the processes of glycolysis, the citric acid cycle, and oxidative phosphorylation. How do these pathways work together to extract energy from glucose?
  \vspace{8em}

  \item Discuss the differences between saturated, unsaturated, and trans fats. Explain their chemical structures, food sources, and effects on health, particularly cardiovascular health.
  \vspace{8em}

\end{enumerate}

\end{document}