\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{amsmath, amssymb}
\usepackage{hyperref}

\setlist[enumerate]{itemsep=0.8em, topsep=0.8em}
\setlist[itemize]{itemsep=0.3em, topsep=0.3em}

\begin{document}

\begin{center}
  {\Large \textbf{Computer Networks}}\\[0.25em]
  {\large \textbf{TCP/IP and Network Architecture Quiz}}\\[0.5em]
\end{center}

\noindent\textbf{Instructions:}
\begin{itemize}
  \item Answer all questions.
  \item For Questions 1--5, choose the best option.
  \item For Questions 6--8, mark True or False.
  \item For Questions 9--10, write detailed answers with diagrams where helpful.
\end{itemize}

\vspace{0.5em}

\begin{enumerate}[label=\textbf{\arabic*.}]
  \item Which layer of the OSI model is responsible for routing packets between networks?
  \begin{enumerate}[label=(\Alph*)]
    \item Data Link Layer
    \item Network Layer
    \item Transport Layer
    \item Session Layer
  \end{enumerate}

  \item TCP provides reliable data transfer through:
  \begin{enumerate}[label=(\Alph*)]
    \item Broadcasting to all nodes
    \item Acknowledgments and retransmissions
    \item Connectionless communication
    \item Fixed packet sizes only
  \end{enumerate}

  \item What is the primary function of DNS?
  \begin{enumerate}[label=(\Alph*)]
    \item Encrypting network traffic
    \item Translating domain names to IP addresses
    \item Assigning IP addresses dynamically
    \item Routing packets across networks
  \end{enumerate}

  \item Which protocol operates at the Transport Layer and provides connectionless, unreliable service?
  \begin{enumerate}[label=(\Alph*)]
    \item TCP
    \item UDP
    \item IP
    \item HTTP
  \end{enumerate}

  \item A subnet mask of 255.255.255.0 (/24) allows for how many usable host addresses?
  \begin{enumerate}[label=(\Alph*)]
    \item 256
    \item 254
    \item 255
    \item 128
  \end{enumerate}

  \item ARP (Address Resolution Protocol) maps IP addresses to MAC addresses. (True/False)

  \item HTTP/2 requires the use of TLS encryption for all communications. (True/False)

  \item A switch operates at the Network Layer and makes forwarding decisions based on IP addresses. (True/False)

  \item Compare and contrast TCP and UDP. Discuss their characteristics, use cases, and explain why certain applications prefer one protocol over the other.
  \vspace{8em}

  \item Explain the TCP three-way handshake process. Describe each step and the purpose of the SYN, SYN-ACK, and ACK messages. What happens if a packet is lost during this process?
  \vspace{8em}

\end{enumerate}

\end{document}